---
output: 
  pdf_document:
    template: preprint_template.tex
    fig_caption: true
    keep_tex: false
    citation_package: natbib
  word_document: 
    reference_docx: doc_template.docx
title: "Spatial patterns in critical thermal limits of diaptomid copepods are shaped by acclimation"
author:
  - name: Austin Hoffman
    affiliation: University of Massachusetts Lowell
    location: 
  - name: Matthew Sasaki
    affiliation: University of Massachusetts Lowell
    location: 
abstract: "ABSTRACT HERE."
keywords: "acclimation, plasticity, copepod, thermal limits, warming tolerance, freshwater"
contact: "**Correspondance**: Matthew_Sasaki@uml.edu" 
current: "This preprint is current as of `r format(Sys.time(), '%B %d, %Y')`"
repo: "**Code**: https://github.com/ZoopEcoEvo/diapt_ctmax_survey.git"
bibliography: references.bib
biblio-style: bib-style
geometry: margin=1in
fontsize: 10pt
graphics: yes
header-includes: 
  \usepackage{caption}    
  \captionsetup[figure]{font=small, margin=20pt, justification=centering}
  \captionsetup[table]{font=small, margin=20pt, justification=centering}
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
editor_options: 
  markdown: 
    wrap: 72
---

```{r echo = F}
if(knitr::is_latex_output()){
  knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  collapse = T)
}
```

# Introduction

1.  Freshwater Biodiversity

-   freshwater bodies are relative microcosms that support massive
    biodiversity
    -   these bodies can and should be focused on to help provide a
        snapshot about how the changing environment is responded to by
        its player
-   previous literature has scratched the surface with fish studies
    -   but there is a general dearth in the literature surrounding
        freshwater biodiversity
-   climate change implications
    -   lethal thermal limits
    -   temperature changes & heat waves
    -   state of climate change in lentic systems

2.  Ecological Importance of Copepods, Generally

-   dominant freshwater zooplankton
    -   nutrient cycling
    -   trophic interactions
-   but thermal limits are less understood
    -   will likely impact their survivorship which has larger
        ecological implications
-   they can serve as great model systems
    -   not only because of lab maintenance capabilities
    -   exhibit plasticity
    -   short generations

3.  Particular Importance of Diaptomids

-   widespread

    -   found consistently throughout most of the contiguous US

        -   further, their widespread nature allows for testing of
            ecological gradients (elevational, latitudinal) to
            investigate their impacts on thermal limits

-   diverse

    -   monophyletic group (Skisto), but 8 distinct species
    -   ecological important

-   dominant zooplankton in many freshwater ecosystems

-   altogether allows for robust investigations of how thermal limits
    may be plastic interspecifically as well as intraspecifically within
    the genus

-   MP1: variation interspecifically due to plasticity so there may be
    shifts in vulnerability

-   MP2: increased freshwater temperatures via ClCh allows for potential
    range shifting of Skistodiaptomus

# Methods

## Collection

## Culturing

## CTmax measurements

## Statistical Analysis

# Results

```{r, figure, echo = F, out.width="100%"}
#| fig.cap = "CAPTION HERE."

plot(1)
#knitr::include_graphics("../Output/markdown/Figures/_PATH_") #Use this when filling in figures from analysis 
```

```{r, table, echo = F}
knitr::kable(x = 1, #Replace 1 with whatever object you want included as a table
      digits = 3, align = "c",
      caption = "CAPTION HERE")
```

# Discussion

1. Plasticity vs Adaptation
  -   MP1: variation interspecifically due to plasticity so there may be
    shifts in vulnerability
    - plasticity
      - reiterate plasticity role in mitigating climate change
        - explain how plasticity can be used to bolster vulnerability
        - inability to respond plastically may result in increased mortality
    - acclimation
      - reiterate how acclimation contrasts with plasticity

2. Range Distributions and Invasions
  -   MP2: increased freshwater temperatures via ClCh allows for potential
    range shifting of Skistodiaptomus
    - reiterate that Ctmax measurements did not significantly differ between the CP and OP populations
      - contrast this with potential Skisto species variation in regards to Ctmax in conjuction with the differential collection temperature

    
3. Future Directions
  - 


4. Conclusion
  - closes gap in copepod literature regarding thermal limits
  - shows the potential for Skistodiaptomids and Diaptomids generally as a model system
    
\newpage

\beginsupplement

# Supplementary Material

```{r supp-fig-1, echo = F, out.width="100%"}
#| fig.cap = "CAPTION HERE."

plot(1)
#knitr::include_graphics("../Output/Figures/_PATH_") #Use this when filling in figures from analysis 
```
