---
output: 
  pdf_document:
    template: preprint_template.tex
    fig_caption: true
    keep_tex: false
    citation_package: natbib
  word_document: 
    reference_docx: doc_template.docx
title: "Spatial patterns in critical thermal limits of diaptomid copepods are shaped by acclimation"
author:
  - name: Austin Hoffman
    affiliation: University of Massachusetts Lowell
    location: 
  - name: Matthew Sasaki
    affiliation: University of Massachusetts Lowell
    location: 
abstract: "ABSTRACT HERE."
keywords: "acclimation, plasticity, copepod, thermal limits, warming tolerance, freshwater"
contact: "**Correspondance**: Matthew_Sasaki@uml.edu" 
current: "This preprint is current as of `r format(Sys.time(), '%B %d, %Y')`"
repo: "**Code**: https://github.com/ZoopEcoEvo/diapt_ctmax_survey.git"
bibliography: references.bib
biblio-style: bib-style
geometry: margin=1in
fontsize: 10pt
graphics: yes
header-includes: 
  \usepackage{caption}    
  \captionsetup[figure]{font=small, margin=20pt, justification=centering}
  \captionsetup[table]{font=small, margin=20pt, justification=centering}
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

```{r echo = F}
if(knitr::is_latex_output()){
  knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  collapse = T)
}
```

# Introduction

1. Copepod Introduction
  *highly abundant
  *crucial role in food webs
  *Skistodiaptomus intro
    *freshwater diaptomids
    *comparatively less studied than other highly abundant freshwater copes
    *the extent of their known phylogeny is distributed in US across diff environment scales (elevation, latitudinal)
    *novel genus for understanding thermal tolerance in freshwater
2. Thermal limits
  *described in a diverse scope across animals, however, copes are underrepresented comparatively especially freshwater
  *what patterns of thermal tolerance are conserved in this diaptomid phylogeny across 8 species and environmental gradients
  *sources of differentiation in thermal limits
    *Plasticity - capacity of plastic response and also rate of its success (perhaps mention Nathan's acclimation experiment)
    *(evidence suggests their are robust clades within Skistodiaptomus genus that may confer different thermal tolerance success)
3. This Study
  *collected CTmax, body size, and fecundity from different populations of Skistodiaptomus
  *Skistodiaptomus pallidus as the focus for comparing the populations from Centennial park and Ochsner Pond
  *this study presents some of the first evidence of how Skistodiaptomus populations from different elevations and latitudes seems to exhibit no significant variation in CTmax
  *further genetic investigation into potential differences
  
# Methods

## Collection

## Culturing

## CTmax measurements

## Statistical Analysis

# Results

```{r, figure, echo = F, out.width="100%"}
#| fig.cap = "CAPTION HERE."

plot(1)
#knitr::include_graphics("../Output/markdown/Figures/_PATH_") #Use this when filling in figures from analysis 
```

```{r, table, echo = F}
knitr::kable(x = 1, #Replace 1 with whatever object you want included as a table
      digits = 3, align = "c",
      caption = "CAPTION HERE")
```

# Discussion

\newpage

```{=tex}
\beginsupplement
```
# Supplementary Material

```{r supp-fig-1, echo = F, out.width="100%"}
#| fig.cap = "CAPTION HERE."

plot(1)
#knitr::include_graphics("../Output/Figures/_PATH_") #Use this when filling in figures from analysis 
```
